\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx,booktabs}
\usepackage{textcomp,url,hyperref}
\hypersetup{
    colorlinks=true,
    citecolor=blue,
    filecolor=blue,
    urlcolor=blue,
    pdfpagemode=FullScreen,
}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}
    \makeatletter
    \newcommand{\linebreakand}{%
      \end{@IEEEauthorhalign}
      \hfill\mbox{}\par
      \mbox{}\hfill\begin{@IEEEauthorhalign}
    }
    \makeatother

\title{Forex Forecasting*\\
{\footnotesize \textsuperscript{*}Note: All authors contributed equally to this project}
}

\author{\IEEEauthorblockN{Eustathios Kotsis}
\IEEEauthorblockA{\textit{StudentID: 7115152200008} \\
\textit{efstathkot@di.uoa.com}\\
}
\and
\IEEEauthorblockN{Michael Darmanis}
\IEEEauthorblockA{\textit{StudentID: 7115152200004} \\
\textit{mdarm@di.uoa.com}\\
}
\and
\IEEEauthorblockN{Vasilios Venieris}
\IEEEauthorblockA{\textit{StudentID: 7115152200017} \\
\textit{vvenieris@di.uoa.com}
}
}

\maketitle

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
time series analysis, forex forecasting, exponential smoothing, autoregressive integrated moving average, convolutional neural netwrorks, recurrent neural networks, hybrid methods 
\end{IEEEkeywords}

\section{Introduction}


\section*{Acknowledgments}

This report was typeset using \LaTeX, originally developed by Leslie Lamport and based on Donald Knuth's \TeX. A template that can be used to format documents with this look and feel has been released under the \href{https://www.ieee.org/publications/subscriptions/info/licensing.html}{\textsc{IEEE License}}, and can be found online at \url{https://www.overleaf.com/latex/templates/ieee-conference-template/grfzhhncsfqn}.

\begin{thebibliography}{00}
\bibitem{m4} S. Makridakis, E. Spiliotis, and V. Assimakopoulos, ``The M4 Competition: 100,000 time series and 61 forecasting methods,'' Int. J. Forecasting, vol. 36, no. 1, pp. 54--74, 2020. \url{https://doi.org/10.1016/j.ijforecast.2019.04.014}
\bibitem{es-rnn} S. Smyl, ``A hybrid method of exponential smoothing and recurrent neural networks for time series forecasting,'' Int. J. Forecasting, vol. 36, no. 1, pp. 75--85, 2020. \url{https://doi.org/10.1016/j.ijforecast.2019.03.017}
\bibitem{winters} P. R. Winters, ``Forecasting sales by exponentially weighted moving averages,'' Management science, vol. 6, no. 3, pp. 324--342, 1960. \url{https://doi.org/10.1287/mnsc.6.3.324}
\bibitem{e-cnn} A.P. Wibawa, A.B.P. Utama, H. Elmunsyah, et al., ``Time-series analysis with smoothed Convolutional Neural Network,'' J Big Data, vol. 9, pp. 44, 2022. \url{https://doi.org/10.1186/s40537-022-00599-y}
\bibitem{slawek} [Online] Available: \url{https://www.uber.com/en-GR/blog/m4-forecasting-competition/}. ``M4 Forecasting Competition: Introducing a New Hybrid ES-RNN Model.''
\end{thebibliography}


\end{document}